---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a) Questions for BAYKAL HAFIZOĞLU

In which situations is it more effective for a technical staff member to customize a product for different users?\
A) When all users have the same needs\
**B) When different users have different needs**\
C) When the product has completely fixed features\
D) When the technical staff member is not authorized to customize

What are the advantages of customizing a product or service according to the needs of various users? What challenges might be encountered in this process?

**Answer :** Customizing according to user needs increases customer satisfaction, making the product more useful and appropriate. Additionally, customization can provide a competitive advantage. However, this process may face challenges such as technical difficulties, increased time and costs, and managing different user demands.

# (b) Tasks

**Libraries used :**

```{r}
library(readr)
library(knitr)
library(kableExtra)
library(dslabs)
```

**Printing the first 10 rows of table. In this part we use kableExtra library to get more readable output :**

```{r}
data("polls_us_election_2016")  

# Display the first 10 rows in table format
polls_us_election_2016 %>%
  head(10) %>%
  kable("html") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))

```

**Showing the total NA values in dataset :**

```{r}
total_na <- sum(is.na(polls_us_election_2016))
total_na

```

**Replacing NA in numeric columns with 1999 and replacing NA in character columns with "Ahmet":**

```{r}

# Load the necessary library and dataset
library(dslabs)
data("polls_us_election_2016")

# Create a new object to store the modified dataset
modified_polls <- polls_us_election_2016

# Replace NA values
modified_polls[] <- lapply(modified_polls, function(col) {
  if (is.numeric(col)) {
    col[is.na(col)] <- 1999  # Replace NA in numeric columns with 1999
  } else if (is.character(col)) {
    col[is.na(col)] <- "Ahmet"  # Replace NA in character columns with "Ahmet"
  } else if (is.factor(col)) {
    col <- as.character(col)  # Convert factors to character
    col[is.na(col)] <- "Ahmet"  # Replace NA in character columns with "Ahmet"
    col <- as.factor(col) 
  }
  return(col)
})

```

**Checking the number of NA values :**

```{r}
total_na <- sum(is.na(modified_polls))
total_na
```

**Printing the modified table :**

```{r}
modified_polls %>%
  head(10) %>%
  kable("html") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
```
